\newglossaryentry{cloud}{
	name={cloud computing},
	description={
		Cloud computing is the term used to refer to a model of network computing where a program or application
		runs on a connected server or servers rather than on a local computing device.
		The computing process may run on one or many connected computers at the same time, utilizing the concept of virtualization. 
	}
}

\newglossaryentry{driver}{
	name={driver},
	description={
		A device driver is a computer program that controls a particular type of device that is attached to a computer.
		Virtual device drivers are variants used to emulate a hardware device in virtualization environments.
	}
}

\newglossaryentry{hypervisor}{
	name={hypervisor},
	description={
		A hypervisor is a piece of computer software that creates and runs virtual machines.
		Type 1 (or native, bare metal) hypervisors run directly on the host's hardware to control the hardware and to manage guest operating systems.
		Type 2 (or hosted) hypervisors run within a conventional operating-system environment.
	}
}

\newglossaryentry{kernel}{
	name={kernel},
	description={
		The  kernel is a program that manages input/output requests from software and translates them into data processing instructions for components of a computer.
		The kernel is a fundamental part of the operating system.
	}
}

\newglossaryentry{ocaml}{
	name={OCaml},
	description={
		OCaml is the most popular variant of the Caml language.
		It is a general-purpose programming language, designed with program safety and reliability in mind.
		OCaml supports functional, imperative, and object-oriented programming styles.
	}
}

\newglossaryentry{trie}{
	name={prefix tree},
	description={
		A prefix tree is an ordered tree data structure that is used to store a dynamic set where the keys are usually strings.
		The key associated to a node is not stored in the tree but defined by its position.
	}
}

\newglossaryentry{unikernel}{
	name={unikernel},
	description={
		Unikernels are single-purpose appliances that are compile-time specialised into
		standalone kernels, and sealed against modification when deployed to a cloud platform.
 	}
}

\newglossaryentry{virtmachine}{
	name={virtual machine},
	description={
		A virtual machine (or VM for short) is a software implementation of a computer that executes programs like a real machine. 
		A single physical machine can be virtualized to create several virtual machines. 
	}
}

\newglossaryentry{xen}{
	name={Xen},
	description={
		The Xen Project hypervisor is an open-source baremetal hypervisor,
		which makes it possible to run many instances of an operating system
		or indeed different operating systems in parallel on a single machine (or host).
	}
}
